\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}


%====================
% EXPERIENCE 4
%====================
\subsection{{Fault tolerance sharded K/V storage system with map reduce  \hfill 2021}}
% \subtext{company A \hfill somewhere, state}
\begin{zitemize}
    \item A fault-tolerant K/V storage system that can serve a big chunk of data with low latency.
    \item Simplified and implemented a Raft protocol.
    \item Designed and implemented sharding algorithm and shard controler. By default, it would split datas evenly on all edges. User can also decided the location for each shard of data as their need.
    \item Designed and implemented data migrating algorithm. In my design, during the data migration, servers can still safely work and reply to clients.
    \item Introduced google map reduce to this system.
\end{zitemize}



%====================
% EXPERIENCE 3
%====================
\subsection{{Milestone  \hfill 2021}}
% \subtext{company A \hfill somewhere, state}
\begin{zitemize}
    \item A Andorid game developed in Java.
    \item Users from all over the world can play against each other, or be teamates.
\end{zitemize}


%====================
% EXPERIENCE 2
%====================
\subsection{{Extracting Amplicon Reads from a Whole Shotgun Metagenomic Dataset  \hfill 2020}}
% \subtext{company C \hfill somewhere, state}
\begin{zitemize}
    \item Designed and implemented a tool for DNA sequencing, and amplicon reads extracting.
    \item Designing, building, and maintaining the SQLite database.
    \item Creating interfaces and scripts to link different parts of the application.
    \item Designing algorithms for sorting and sequencing.
\end{zitemize}


%====================
% EXPERIENCE 1
%====================
\subsection{{Peer-to-peer chatting App \hfill 2018}}
% \subtext{company B \hfill somewhere, state}
\begin{zitemize}
    \item Designed and implemented an application that allows users to do peer-to-peer chatting directly.
    \item Provides users with a low latency, high transfering speed chatting experience.
    \item Protect user's privacy by never collecting user data.
\end{zitemize}


\end{document}